---
title: "Cutting Data by Risk Regions"
author: "Emma Sharpe"
date: "3/19/2021"
output:
  html_document:
    code_download: true
    df_print: paged
    keep_md: true
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
---
In this document I am cutting the San Francisco Estuary institute (SFEI) microplastic data to the boundaries of the study site and risk regions. To learn more about how the microplastic data was collected, read the [SFEI microplastic report](https://www.sfei.org/documents/understanding-microplastics).

# Required packages
```{r }
library(IETC) # To load packages use > devtools::install_github("WWU-IETC-R-Collab/IETC")
library(tidyverse)
library(data.table)
library(sf)
library(knitr)
```

# Loading data and shapefiles 

```{r}
# Read in SFEI particle data zipfile created in ClipToProjectBoundary and unzip it.
particles <- IETC::unzipShape("https://github.com/WWU-IETC-R-Collab/ClipToProjectBoundary/raw/main/SFEI.particles.locations.zip")
```

Next we want to read in the shapefile we are going to use to cut the data. This shapefile is the risk regions selected for the study site. 
```{r}
# Unzip the shapefile from the GitHub repository "Risk_Region.shapefile"
unzipShape("https://github.com/NSF-Microplastics-Project/Risk_Region.shapefile/raw/main/Data/SFB_RiskRegions_20210304_SP.zip")

# The code below is not related to above but is indicating the zipfolder in this working directory. I am taking out the .shp to be use when cutting the data. 

SFB.riskregions <- st_read("SFB_RiskRegions_20210304_SP/SFB_RiskRegions_20210304_SP.shp") %>% # transforms shapefile CRS to WGS84 vs NAD83
  st_transform(st_crs(particles))
```



# Data Before Cutting 

```{r}
ggplot() +
  geom_sf(data = SFB.riskregions) +
  geom_sf(data = particles, color = "blue")
```



```{r}
particles.within <- particles[SFB.riskregions,] # subsets only data within project study area

ggplot() +
  geom_sf(data = SFB.riskregions) +
  geom_sf(data = particles.within, color = "blue")
```

